### 2019-06-28 papers/journal/intro.tex
Minor update in intro and addition of the rebuttle letter

\noindent 
%A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
The cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the
nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
%These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
%%The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
%%Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
%%Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
%%However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
%%In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
%
Cargo is moved between these organelles in small membrane-bound
transporters known as vesicles \cite{stenmark2009rab}.
%s

This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
%
Membrane traffic underpins nearly every aspect of eukaryotic cellular
physiology, including human cellular physiology.
%
Defects in membrane traffic lead to a variety of disorders or even
cell death \cite{stenmark2009rab}.
%
Understanding how membrane traffic functions is therefore one of the
central challenges of cell biology.
%
Some progress has been made, as cell biologists have assembled a
“parts list” of molecules that drive vesicle
traffic~\cite{dacks2007evolution}.
%
The essential processes involve the creation of vesicles loaded with
cargo from source organelles, known as “budding”, and the depositing
of those vesicles and cargo into target organelles, known as “fusion”
\cite{munro2004organelle}.
%
Budding is regulated by proteins known as coats and adaptors that
select cargo.
%
Fusion is regulated by proteins known as SNAREs and tethers, that
ensure that vesicles fuse to the correct target
\cite{mani2016stacking}.
%
Although we know a great deal about molecular-level details, there has
been very little work done on how such processes are integrated across
scales to build the entire vesicle traffic system (VTS).
%
We have recently attempted to use ideas of graph theory to address
this question \cite{mani2016stacking,shukla2017discovering}.

@@

In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset. 
%
We would also like to directly make statements about steady state properties, rather
than using transition dynamics to the first search for steady states. 
%
Formal verification tools like model checkers, SAT and SMT solvers serve precisely this purpose. 
%
Formal verification tools, such as model checkers
\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
	cimatti2000nusmv, holzmann1997model} and SAT solvers
\cite{moskewicz2001chaff,een2004extensible} serve precisely this
purpose.
%
The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
%

%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
\subsection{Previous work and our Contribution}
In a recent work, we employed the model checker CBMC \cite{CKY03,
	ckl2004} meant to analyze ANSI C programs for studying this problem.
%
In this work, VTSs and SNARE regulations were modeled as C code mostly
using arrays to represent graphs and boolean tables.
%
Queries about graph connectivity requirements for different variations
of SNARE Regulations were modeled as logical assertions to be checked
by the model checker.
%
CBMC uses its own built-in encodings to reduce the analysis problem to
boolean satisfiability problem which is solved using SAT solvers.
%
This work was successful in demonstrating the feasibility of this
technology to this domain.
%
However, the scalability of this approach was limited (up to VTSs
with 7-8 nodes) due to the following reasons:
\begin{enumerate}
	\item The encoding used to model VTSs was not completely fine-tuned
	to the structure of the problem.
	\item The queries to be solved involve quantified formulas, i.e., we
	needed to solve queries of the form ``\emph{for all} graphs does there
	\emph{exist} SNARE regulation constraints that satisfy biological
	steady state.
\end{enumerate} As CBMC does not directly support solving such
quantified formulas, we had to use a technique that combined
non-determinism and partial enumeration that is not as
efficient.\newline

>>>>

\noindent 
%A characteristic feature of eukaryotic cells is the presence of multiple internal membrane-bounded compartments. 
The cytoplasm of all eukaryotic cells is broken up into distinct membrane-bound locations known as organelles: the
nuclear membrane, endoplasmic reticulum (ER), Golgi apparatus, vacuoles and lysosomes are examples of these.
%These compartments exchange molecules amo\-ngst themselves in small membrane-bounded packets called vesicles~\cite{alberts2002molecular}. 
%
%%The molecular interaction network that controls the vesicle traffic system involves dozens of varieties of molecules that regulate the flow of cargo. 
%
%%Due to this, obtaining a complete understanding of the VTS through physical experimentation alone is a hard problem.
%
%%Highly reduced models of vesicle traffic have previously provided insight into how the chemical composition of various cellular compartments can emerge out of molecular regulation and cargo flow. 
%
%%However, the high complexity of problems in VTS restricts the use of traditional methods like simulation and statistical reasoning~\cite{mani2016stacking}. 
%The high complexity of problem restricts the use of traditional methods like simulation and statistical reasoning and the requirement of precise analysis makes formal methods an ideal candidate. 
%%In this paper, using formal methods, we solve the problem of completing incomplete VTS graphs while also considering constraints due to molecular interactions, thereby demonstrating the effectiveness of such methods.
%
%
Cargo is moved between these organelles in small membrane-bound
transporters known as vesicles \cite{stenmark2009rab}.
%
This organization resembles a transport logistics network, and is commonly known as the membrane traffic system.
%
Membrane traffic underpins nearly every aspect of eukaryotic cellular
physiology, including human cellular physiology.
%
Defects in membrane traffic lead to a variety of disorders or even
cell death \cite{stenmark2009rab}.
%
Understanding how membrane traffic functions is therefore one of the
central challenges of cell biology.
%

Some progress has been made, as cell biologists have assembled a
“parts list” of molecules that drive vesicle
traffic~\cite{dacks2007evolution}.
%
The essential processes involve the creation of vesicles loaded with
cargo from source organelles, known as “budding”, and the depositing
of those vesicles and cargo into target organelles, known as “fusion”
\cite{munro2004organelle}.
%
Budding is regulated by proteins known as coats and adaptors that
select cargo.
%
Fusion is regulated by proteins known as SNAREs and tethers, that
ensure that vesicles fuse to the correct target
\cite{mani2016stacking}.
%
Although we know a great deal about molecular-level details, there has
been very little work done on how such processes are integrated across
scales to build the entire vesicle traffic system (VTS).
%
We have recently attempted to use ideas of graph theory to address
this question \cite{mani2016stacking,shukla2017discovering}.

@@

In contrast, here we seek understand properties of vesicle traffic networks over all possible update rules, not just for a sampled subset.
%
Formal verification tools like model checkers, SAT,  SMT and QBF solvers serve precisely this purpose. 
%
%Formal verification tools, such as model checkers
%\cite{clarke1996symbolic, biere2003bounded, clarke2008birth,
%	cimatti2000nusmv, holzmann1997model} and SAT solvers
%\cite{moskewicz2001chaff,een2004extensible} serve precisely this
%purpose.
%%
The tools model the computation symbolically for the graphs of finite size and can make a prediction about the hypothesis for all possible states of the system without explicit enumeration of rules. 
%

%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
\subsection{Previous work and our Contribution}

As CBMC does not directly support solving such
quantified formulas, we had to use a technique that combined
non-determinism and partial enumeration that is not as
efficient.\newline
